Investigating for Bias in Houston, Texas Police Citations

### 2023-04-20 FinalReport.Rmd
slay shawty

#mini_htx <- read_csv("Datasets/mini_htx.csv")
full_htx <- read_csv("/Users/virginiabaskin/Downloads/tx_houston_2023_01_26.csv") #was full_htx
# census_csv <- read_csv("/Users/virginiabaskin/Downloads/Census Data Houston.csv")
mini_htx <- full_htx[seq(1,2000000,3),]
mini_htx <- mini_htx %>% rename("Beats" = "beat")
beats_data <- read_csv("Datasets/COH_POLICE_BEATS.csv")
# htx_stats <- read_csv("Datasets/DECENNIALPL2020.P2-2023-03-02T224324.csv")
#dbWriteTable(con, "census", census_csv, overwrite = TRUE)

@@

## Distribution Over Time
First, we began our exploration by looking at the distribution of citations over time. We first visualized citations issued to each race over the years 2014-2020 in order to evaluate the consistency of the distribution of citations over time.
```{r Race Line Graph by Year, echo=FALSE}
# Visualize totals for each race by year
# Grace

@@

Next in our investigation of citations throughout time, we decided to visualize the number of citations issued throughout the hours of the day.
```{r Line graph of number of citations vs. Hour in Day, echo=FALSE}
# Observe citations over time and any time-associate patterns
time <- as.POSIXct(mini_htx$time, format = "%H:%M:%S")
hour <- as.numeric(format(time, "%H"))
count <- data.frame(table(na.omit(hour)))
plot(count$Var1, count$Freq, type = "n", xlab = "Hour", ylab = "Frequency of Citations", main = "Frequency of Citations vs Hour in Day")
lines(count$Var1, count$Freq, type = "l", lwd = 2)
```

>>>>

#mini_htx <- read_csv("Datasets/mini_htx.csv")
full_htx <- read_csv("/Users/virginiabaskin/Downloads/tx_houston_2023_01_26.csv")
# census_csv <- read_csv("/Users/virginiabaskin/Downloads/Census Data Houston.csv")
mini_htx <- full_htx[seq(1,2000000,3),]
mini_htx <- mini_htx %>% rename("Beats" = "beat")
beats_data <- read_csv("Datasets/COH_POLICE_BEATS.csv")
# htx_stats <- read_csv("Datasets/DECENNIALPL2020.P2-2023-03-02T224324.csv")
#dbWriteTable(con, "census", census_csv, overwrite = TRUE)

@@

## Distribution Over Time

First, we began our exploration by looking at the distribution of citations over time. We first visualized citations issued to each race over the years 2014-2020 in order to evaluate the consistency of the distribution of citations over time.

```{r Race Line Graph by Year, echo=FALSE}
# Visualize totals for each race by year
# Grace

@@

Next in our investigation of citations throughout time, we decided to visualize the number of citations issued throughout the hours of the day.

```{r Line graph of number of citations vs. Hour in Day, echo=FALSE}
# Observe citations over time and any time-associate patterns
time <- as.POSIXct(mini_htx$time, format = "%H:%M:%S")
hour <- as.numeric(format(time, "%H"))
count <- data.frame(table(na.omit(hour)))
plot(count$Var1, count$Freq, type = "n", xlab = "Hour", ylab = "Frequency of Citations", main = "Frequency of Citations vs Hour in Day")
lines(count$Var1, count$Freq, type = "l", lwd = 2)
```
